Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility

### 2025-11-22 paper/01-introduction.qmd
Up V2

What is the legitimate scope of market inequality in the eyes of the public? Since the early 1980s, many countries have experienced a rollback of universal welfare programs and a shift toward the privatisation and commodification of public goods and social services [@gingrich_making_2011; @streeck_how_2016]. In Latin America, these reforms extended market logic into domains of social reproduction long governed by the state, shrinking public provision and expanding private actors in core welfare sectors [@ferre_welfare_2023]. From a moral-economy perspective, this diffusion of market rules has reconfigured the normative order: through policy feedback, welfare institutions increasingly embed market-based criteria of “fair” allocation and shape how citizens understand deservingness and the balance between state and market [@svallforsMoralEconomyClass2006a; @koos_moral_2019]. Against this backdrop, growing scholarship examines *market justice preferences*—the extent to which citizens regard market-based criteria as a fair basis for access to essential services such as healthcare, education and pensions [@castillo_perceptions_2025; @svallfors_political_2007; @lindh_public_2015]. These orientations matter because they help legitimise economic inequality by portraying stratified outcomes as a fair result of individual responsibility and limited state intervention.

This article examines public support for the commodification of pension welfare—specifically, whether people consider it fair that access to better pensions depends on income or contributions. Pension privatisation lies at the core of Latin America’s trajectory of commodification [@huber_political_2000], making pension systems a strategic domain for analysing how market principles become normatively embedded [@mau_inequality_2015]. As many countries expanded mandatory or voluntary individual-capitalisation schemes—most radically in Chile—pensions became organised around contribution-based entitlements and market performance [@arenas_sistemas_2019; @verbic_political_2019]. This shift reshapes not only how pension institutions allocate old-age risk, heightening exposure to poverty in retirement and tying benefit levels to lifetime labour-market trajectories [@oecd_pensions_2023; @madero-cabib_private_2019], but also reshape the justice principles citizens associate with old-age security: people have to judge whether higher benefits should follow market-derived criteria or solidaristic principles [@arrizabalomontoro_debate_2019; @borzutzky_pension_2012]. Although we know something about what people consider a “just” monetary pension [@castillo_deserving_2019] and about support for public versus private provision [@busemeyer_welfare_2020; @jaime-castillo_public_2013], we still lack systematic evidence on how citizens assess the fairness of market-dependent access to pensions.

Research shows that support for market-based access to welfare services is strongly stratified: individuals with higher income, education or class position are more likely to endorse market-based criteria than disadvantaged groups [@busemeyer_skills_2014; @immergut_it_2020;  @lindh_public_2015;  @svallfors_political_2007]. Evidence for pensions points in the same direction: higher income and greater financial gains in funded schemes correlate with stronger support for market-oriented pension policies [@kerner_pension_2020]. Yet we know very little about how movement within the class structure shapes preferences for pension commodification. This gap is especially salient in Latin America, where mobility has unfolded under high inequality and deeply privatised welfare regimes [@lopez-roldan_comparative_2021]. Social origins and destinations anchor material interests and justice principles [@alesina_intergenerational_2018; @langsaether_explaining_2022; @gugushvili_subjective_2017], while movement between these positions exposes individuals to new risks, resources and normative environments that reshape fairness judgements [@gugushvili_trends_2014; @helgason_longterm_2023]. As @mau_inequality_2015 argues, social mobility can foster market-justice orientations, helping explain how inequalities in access to welfare services become normatively sustained.

The literature identifies several mechanisms through which mobility may shape distributive-justice preferences—material self-interest [@benabou_social_2001], socialisation and acculturation [@jaime-castillo_social_2019], learning through long-term exposure [@helgason_longterm_2023], and cognitive attributions such as self-serving bias or privilege awareness [@gugushvili_intergenerational_2016c; @molina_its_2019]. While distinct, these accounts converge in highlighting two broad channels relevant for market-based welfare: shifts in material stakes and shifts in normative frames [@mau_inequality_2015]. In this paper, I do not treat these mechanisms as mediators but use them to guide hypotheses about heterogeneity: if mobility alters preferences through material interests and normative updating, its effects should be most potent among those who interpret social outcomes through merit-based evaluations of effort [@castillo_perceptions_2025; @mijs_belief_2022].

Against this background, this article pursues two aims: first, to assess whether intergenerational mobility causally affects support for the commodification of pensions; and second, to examine whether this effect varies by meritocratic beliefs. I argue that mobility works through two main channels. Upward mobility increases earnings, expected returns in a funded system and perceived economic security, making contribution-based access more appealing. At the same time, integration into higher-class networks exposes people to more individualistic norms and effort-based understandings of fairness. Downward mobility, in turn, heightens economic insecurity, dependence on collective protection and attachment to solidaristic principles, lowering support for market allocation. Meritocratic beliefs are conceptualised not as mediators but as moderators. Among those who see mobility as a fair reward for effort, both material and normative effects should be amplified, producing higher support for pension commodification. The paper contributes to research on market justice by focusing on a specific welfare domain and by providing causal evidence on how mobility shapes distributive preferences.

This study focuses on Chile, a particularly instructive case for examining preferences for pension commodification. Despite sustained economic growth, Chile combines high and persistent inequality with short-range upward mobility and substantial barriers to higher-class positions [@flores_top_2020; @salgado_uplifting_2025; @torche_intergenerational_2014]. It was the first country worldwide to fully replace a public pay-as-you-go system with a mandatory, privately administered (through pension fund administrators, AFPs) defined-contribution scheme, while the state has progressively expanded a segmented solidarity pillar to compensate for insufficient benefits [@madariaga_three_2020; @boccardo_30_2020; @solimano_rise_2021]. In parallel—and despite waves of protest from 2006 to 2019 targeting the AFP system [@somma_no_2021]—Chilean subjectivities have been increasingly shaped by neoliberal discourses and market logics, influencing attitudes toward pension distribution and inequality [@araujo_desafios_2012; @galvez_con_2023]. The combination of profound inequality, market-driven old-age security and contested legitimacy makes Chile a critical case for analysing how mobility and meritocratic beliefs structure support for pension commodification.

To address these questions, the study draws on large-scale, representative survey data for the urban Chilean population collected in 2016, 2018 and 2023. It adopts a causal framework of mobility effects inspired by @breen_effects_2024. The following section outlines the theoretical framework linking preferences for market-based welfare, social mobility and expected heterogeneity by meritocratic beliefs and time, and derives hypotheses. A subsequent section presents the causal identification strategy, the data, the variables, and the analytical approach. The empirical sections report the findings and interpret their implications. The article concludes by discussing what these results reveal about the politics of market-based pension welfare and social mobility.

>>>>

What is the legitimate scope of market inequality in the eyes of the public? Since the early 1980s, many countries have experienced a rollback of universal welfare programs and a shift toward the privatisation and commodification of public goods and social services [@gingrich_making_2011; @streeck_how_2016]. In Latin America, these reforms extended market logic into domains of social reproduction long governed by the state, shrinking public provision and expanding private actors in core welfare sectors [@ferre_welfare_2023]. From a moral-economy perspective, this diffusion of market rules has reconfigured the normative order: through policy feedback, welfare institutions embed market-based criteria of “fair” allocation and shape how citizens understand deservingness and the balance between state and market [@svallforsMoralEconomyClass2006a; @koos_moral_2019]. Against this backdrop, growing scholarship examines *market justice preferences*—the extent to which citizens regard market-based criteria as a fair basis for access to essential services such as healthcare, education and pensions [@castillo_perceptions_2025; @svallfors_political_2007; @lindh_public_2015]. These orientations matter because they help legitimise economic inequality by portraying stratified outcomes as a fair result of individual responsibility and limited state intervention.

This article examines public support for the commodification of pension welfare—specifically, whether people consider it fair that access to better pensions depends on income or contributions. Pension privatisation lies at the core of Latin America’s trajectory of commodification [@huber_political_2000]. As many countries expanded mandatory or voluntary individual-capitalisation schemes—most radically in Chile—pensions became organised around contribution-based entitlements and market performance [@arenas_sistemas_2019; @verbic_political_2019]. This shift reshapes how pension institutions allocate old-age risk, tying benefit levels to lifetime labour-market trajectories and increasing exposure to poverty in retirement [@oecd_pensions_2023; @madero-cabib_private_2019]. It also transforms the justice principles citizens associate with old-age security: they must judge whether higher benefits should follow market-derived criteria or solidaristic principles [@arrizabalomontoro_debate_2019; @borzutzky_pension_2012]. Although we know something about what people consider a “just” monetary pension [@castillo_deserving_2019] and about support for public versus private provision [@busemeyer_welfare_2020; @jaime-castillo_public_2013], we still lack systematic evidence on how citizens assess the fairness of market-dependent access to pensions.

Research shows that support for market-based access to welfare services is strongly stratified: individuals with higher income, education or class position are more likely to endorse market-based criteria than disadvantaged groups [@busemeyer_skills_2014; @immergut_it_2020; @lindh_public_2015; @svallfors_political_2007]. Evidence for pensions points in the same direction: higher income and greater financial gains in funded schemes correlate with stronger support for market-oriented pension policies [@kerner_pension_2020]. Yet we know very little about how movement within the class structure shapes preferences for pension commodification. This gap is especially salient in Latin America, where mobility has unfolded under high inequality and deeply privatised welfare regimes [@lopez-roldan_comparative_2021]. Social origins and destinations anchor material interests and justice principles [@alesina_intergenerational_2018; @langsaether_explaining_2022; @gugushvili_subjective_2017], while movement between these positions exposes individuals to new risks, resources and normative environments that reshape fairness judgements [@gugushvili_trends_2014; @helgason_longterm_2023]. Social mobility can thus foster market-justice orientations, helping explain how inequalities in access to welfare services become normatively sustained [@mau_inequality_2015].

Existing accounts identify several mechanisms through which intergenerational mobility may shape distributive-justice preferences but converge on two channels particularly relevant for market-based welfare: changes in material stakes and shifts in normative frames [@ares_changing_2020; @jaime-castillo_social_2019; @helgason_longterm_2023; @gugushvili_intergenerational_2016c]. Recent research shows that meritocratic beliefs—seeing that effort and ability are rewarded—are strongly associated with support for market allocation [@castillo_perceptions_2025]. Perceived upward mobility reinforces meritocratic interpretations of success, whereas downward mobility is more closely linked to structural explanations of inequality without necessarily eroding meritocratic convictions [@mijs_belief_2022]. Thus, meritocracy and mobility operate on partly separate tracks yet intersect in systematic ways. I treat meritocratic beliefs as a post-treatment moderator—a diagnostic lens on potential mechanisms. If mobility partly shapes preferences by strengthening merit-based understandings of fairness and altering material stakes, its effects should be most visible—and most pro-market—among individuals who already interpret social outcomes through meritocratic lenses.

This article pursues two aims: first, to assess whether intergenerational occupational mobility causally affects support for the commodification of pensions; and second, to examine whether this effect varies by meritocratic beliefs as a diagnostic of possible transmission channels. I argue that social mobility operates through two main pathways. Upward mobility increases earnings, expected returns in a funded system and perceived economic security, making contribution-based access more appealing. At the same time, exposure to higher-class networks reinforces individualistic and effort-based understandings of fairness. Downward mobility tends to heighten economic insecurity, dependence on public protection and attachment to external attributions of poverty, reducing support for market allocation. Meritocratic beliefs are conceptualised not as mediators but as moderators. Among individuals with stronger meritocratic beliefs, upward mobility should heighten support for market-based access. In contrast, downward mobility should weaken—or even reverse—its usual de-commodifying pattern, as meritocratic interpretations of effort lead individuals to view market outcomes as fair regardless of direction. The paper contributes to research on market justice by identifying the causal effects of mobility and by using meritocracy to probe whether these effects align with a meritocratic channel.

The study focuses on Chile, an instructive case for examining preferences for pension commodification. Despite sustained economic growth, Chile combines high and persistent inequality with short-range upward mobility and substantial barriers to higher-class positions [@flores_top_2020; @salgado_uplifting_2025; @torche_intergenerational_2014]. It was the first country worldwide to fully replace a public pay-as-you-go system with a mandatory, privately administered defined-contribution scheme, while the state has progressively expanded a segmented solidarity pillar to compensate for insufficient benefits [@madariaga_three_2020; @boccardo_30_2020; @solimano_rise_2021]. In parallel—and despite waves of protest from 2006 to 2019 against the private pension system [@somma_no_2021]—Chilean subjectivities have been increasingly shaped by neoliberal discourses and market logics, influencing attitudes toward pension distribution and inequality [@araujo_desafios_2012; @galvez_con_2023]. The combination of profound inequality, market-driven old-age security and contested legitimacy makes Chile a critical case for analysing how mobility and meritocratic beliefs structure support for pension commodification.

To address these questions, the study draws on large-scale, representative survey data for the urban Chilean population collected in 2016, 2018 and 2023. It adopts a causal framework of mobility effects inspired by @breen_effects_2024. The next section outlines the theoretical framework linking preferences for market-based welfare, social mobility and expected heterogeneity by meritocratic beliefs and time, and derives hypotheses. A subsequent section presents the causal identification strategy, the data and the analytical approach. The empirical sections report the findings, and the article concludes by discussing what these results reveal about the politics of market-based pension welfare and social mobility.

### 2025-11-22 paper/02-antecedents.qmd
Up V2

## Market justice preferences

@@

>>>>

## Preferences for market-based welfare

@@

\begin{table}[htbp]
\centering
\caption{Overview of hypotheses with expected directional patterns}
\begin{tabular}{p{3.2cm} p{3.2cm} p{4cm} p{5cm}}
\toprule
\textbf{Hypothesis} & \textbf{Focus} & \textbf{Expected pattern} & \textbf{Interpretation} \\
\midrule
\textbf{H1: Average mobility effect} &
Effect of intergenerational mobility on preferences for pension commodification &
Upward mobility $\uparrow$ higher support; downward mobility $\downarrow$ lower support relative to immobility &
Mobility shapes preferences through material stakes and normative frames \\
\midrule
\textbf{H2a: Upward $\times$ Meritocracy} &
Conditional effect of upward mobility by meritocracy &
Under high meritocracy: amplified pro-market effect $\uparrow\uparrow$; under low meritocracy: modest increase $\uparrow$ &
Meritocratic lenses strengthen pro-market reactions to upward mobility \\
\midrule
\textbf{H2b: Downward $\times$ Meritocracy} &
Conditional effect of downward mobility by meritocracy &
Under low meritocracy: moderate decrease $\downarrow$; under high meritocracy: negative effect attenuated $\searrow$ toward neutral or slightly positive attitudes &
Meritocratic lenses weaken de-commodifying reactions to downward mobility \\
\bottomrule
\end{tabular}
\end{table}

### 2025-11-22 paper/03-methods.qmd
up antes de borrar tiempo
Up V2

$$

ATT_{j,k,j} = E\big[Y(D = k) \mid O = j, D = k \big] - E\big[Y(D = j) \mid O = j, D = k \big]

$$ {#eq-att}

@@

To test heterogeneity in mobility effects, I examine two moderators: meritocratic perceptions and time. Meritocracy is captured with two items [@young_rise_1958], one referring to effort (“In Chile, people are rewarded for their efforts”) and one to talent (“In Chile, people are rewarded for their intelligence and skills”), each answered on a five-point Likert scale (1 = “strongly disagree” to 5 = “strongly agree”). I average the two items into a single index and dichotomize it into low meritocracy (≤ 3) and high meritocracy (≥ 4). Time is measured by survey wave (2016, 2018, 2023) and entered as a categorical (dummy) variable. Both variables are used as moderators by interacting them with the mobility treatment to assess conditional average treatment effects—i.e., whether the effect of mobility varies across levels of meritocratic perceptions or across survey waves.

@@

The specification is doubly robust: entropy-balancing weights are combined with covariate adjustment so consistency holds if either the weighting model or the outcome model is correctly specified, while also improving efficiency [@wooldridge_introductory_2009]. These results are virtually identical to baseline models without covariates (see [Supplementary Material](#anexo) for complete models), with no substantive changes in the mobility coefficients. Heterogeneous effects by meritocratic perceptions and survey wave are examined through interaction models described in the previous section.

>>>>

$$ 
ATT_{j,k,j} = E\big[Y(D = k) \mid O = j, D = k \big] - E\big[Y(D = j) \mid O = j, D = k \big]
$${#eq-att}

@@

To explore whether mobility effects vary across key contextual dimensions, I examine meritocratic perceptions as a moderator. Meritocracy is captured with two items [@young_rise_1958], one referring to effort (“In Chile, people are rewarded for their efforts”) and one to talent (“In Chile, people are rewarded for their intelligence and skills”), combined into a single index and dichotomized into low (≤ 3) and high (≥ 4) meritocracy. Because meritocracy is measured after mobility, it is used not as a causal effect modifier but as a post-treatment moderator to probe potential mechanisms. I estimate interaction models between mobility and meritocracy and report conditional treatment effects (simple slopes) at low and high meritocratic levels.

@@

The specification is doubly robust: entropy-balancing weights are combined with covariate adjustment so consistency holds if either the weighting model or the outcome model is correctly specified, while also improving efficiency [@wooldridge_introductory_2009]. These results are virtually identical to baseline models without covariates (see [Supplementary Material](#anexo) for complete models), with no substantive changes in the mobility coefficients. Heterogeneous effects by meritocratic perceptions are examined through interaction models described in the previous section.

### 2025-11-22 paper/04-analysis.qmd
Up V2

## Effect heterogeneity

To probe potential mechanisms underlying the mobility effects, I estimate origin-specific ATT models that interact the mobility treatment with high meritocratic perceptions (ref. = low), using stabilized IPW weights, covariate adjustment, and wave fixed effects. I also estimate an analogous specification interacting mobility with survey waves (ref. = 2016) to assess temporal heterogeneity in the treatment effect (see [Supplementary Material](#anexo) for complete models).

@@

@fig-interact displays the origin-specific ATT estimates from the meritocracy interaction models as marginal effects of the mobility treatment at low and high meritocratic beliefs. For low-merit respondents, mobility effects are uniformly small and imprecise across trajectories: Low→Middle ($\beta$ = −0.02, 95% CI [−0.09, 0.04]), Low→High ($\beta$ = −0.03, [−0.10, 0.05]), Middle→Low ($\beta$ = −0.00, [−0.07, 0.06]), and a modest, non-significant positive estimate for Middle→High ($\beta$ = 0.07, [−0.01, 0.14]), while downward moves from high origin show borderline negative effects (High→Middle: $\beta$ = −0.07, [−0.15, 0.00]; High→Low: $\beta$ = −0.08, [−0.15, 0.00]). Among high-merit respondents, the pattern is directionally consistent with meritocratic moderation but statistically robust only for one trajectory: the ATT for Middle→High at high merit is positive and significant ($\beta$ = 0.22, [0.05, 0.38]), whereas Low→Middle ($\beta$ = 0.02, [−0.13, 0.16]), Low→High ($\beta$ = 0.02, [−0.15, 0.20]), High→Middle ($\beta$ = −0.10, [−0.28, 0.09]), and High→Low ($\beta$ = −0.22, [−0.44, 0.00]) remain statistically indistinguishable from zero. Overall, these results provide only limited and trajectory-specific evidence that meritocratic beliefs moderate the causal effect of intergenerational occupational mobility on preferences for pension commodification, with a clearer pro-commodification sign only for upward mobility from middle to high status among high-merit respondents.

```{r}
#| label: fig-interact-wave
#| fig-cap: "Effects of intergenerational occupational mobility on preferences for pension commodification, by survey wave. Coefficient plot of origin-specific ATT estimates comparing mobility versus immobility, estimated from interaction models (T × Wave). Points show the marginal effects (simple slopes) of the mobility treatment in 2016, 2018, and 2023; bars are 95% confidence intervals. Estimates from pooled WLS with doubly robust adjustment, wave fixed effects, and standard errors clustered by individual."
#| out-width: '90%'
#| fig-asp: 0.8
#| fig-cap-location: bottom
#| echo: false
#| results: asis

g5+
  theme(legend.text = element_text(size = 10))
```

I find no consistent evidence of heterogeneous causal effects across survey waves. @fig-interact-wave displays the marginal effects of mobility trajectories on market-justice preferences for pensions in 2016, 2018, and 2023. Across trajectories, the estimated ATTs remain small and their confidence intervals largely overlap over time. Upward mobility from middle origin shows a positive and statistically significant effect in 2016 (Middle→High, $\beta$ = 0.13, 95% CI [0.05, 0.22]) and downward mobility from high origin displays negative effects at baseline (High→Middle and High→Low, both $\beta$ ≈ −0.19, CIs excluding zero), but these patterns attenuate and become statistically indistinguishable from zero by 2023. Taken together, the results suggest that any initial pro-commodification response to upward mobility and de-commodifying response to downward mobility are not stable over time, and the causal effect of mobility on preferences for pension commodification is effectively time-invariant over the 2016–2023 period.

>>>>

## The role of meritocracy

To probe whether meritocratic beliefs channel the impact of mobility on preferences for pension commodification, I estimate interaction models between mobility and meritocratic beliefs and examine the conditional treatment effects of mobility at low and high levels of meritocracy (see [Supplementary Material](#anexo) for complete models).

@@

@fig-interact displays the origin-specific ATT estimates from the meritocracy interaction models as marginal effects of the mobility treatment at low and high meritocratic beliefs. Across trajectories, mobility effects for low-merit respondents are uniformly small and imprecise, hovering around zero for both upward and downward moves. Among high-merit respondents, the pattern aligns only partially with the proposed mechanism: upward mobility from middle to high status shows a clear and statistically significant pro-commodification effect ($\beta$ = 0.22, 95% CI [0.05, 0.38]), whereas all other trajectories—Low→Middle, Low→High, Middle→Low, High→Middle, and High→Low—remain statistically indistinguishable from zero or display negative estimates that do not systematically weaken under high merit. Formal interaction tests also fail to detect strong heterogeneity by meritocratic beliefs (see [Supplementary Material](#anexo) for interaction models). Taken together, the results provide only limited support for the mechanism hypothesis: meritocracy appears to amplify the pro-market consequences of upward mobility in one specific trajectory, but there is no general or consistent evidence that meritocratic beliefs constitute a stable channel through which intergenerational mobility shapes preferences for pension commodification.

### 2025-11-22 paper/paper.qmd
Up V2

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
format:
  html: 
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: Andreas Laffert Tamayo
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 My abstract
  \newline
 **Keywords**: Pension commodification · Intergenerational mobility · Causal inference · Meritocracy · Chile
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---

>>>>

---
title: "Preferences for the commodification of pensions in Chile: the rol of intergenerational social mobility"
format:
  html: 
    latex-environment: true
    code-fold: true
    html-math-method: katex
    number-sections: true
    code-link: true
    title-block-banner: true
    theme:
      - pretty.scss
  pdf: 
    pdf-engine: xelatex
    geometry: margin=2cm
    template-partials: 
      - title.tex
    keep-tex: true
    include-in-header:
      text: |
        \usepackage[noblocks]{authblk}
        \renewcommand*{\Authsep}{, }
        \renewcommand*{\Authand}{, }
        \renewcommand*{\Authands}{, }
        \renewcommand\Affilfont{\small}
    number-sections: true
editor: source
bibliography: "../input/bib/tesis-magister.bib"
csl: "../input/bib/apa6.csl"
author:
  - name: Andreas Laffert Tamayo
    orcid: 0000-0002-9008-2454
    email: alaffertt@estudiante.uc.cl 
    affiliations:
      - ref: 1
affiliations: 
  - id: 1
    name: Instituto de Sociología, Pontificia Universidad Católica de Chile
citeproc: true
abstract: | 
 My abstract
  \newline
 **Keywords**: Pension commodification · Intergenerational mobility · Causal inference · Meritocracy · Chile
link-citations: true
linestretch: 1.5
mainfont: Times New Roman
fontsize: 13pt          
colorlinks: true
fig-height: 4
fig-width: 7.5
---
